---
title: 'Week 9: Presentation'
author: "Sonika Mahat"
date: "2025-03-19"
output: 
beamer_presentation:
  theme: "Malmoe"
  colortheme: "beaver"
  fontsize: 12pt
  classoption: "aspectratio = 169"
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  fig.align = 'center'
  )
library(tidyverse)
library(knitr)
install.packages("Cairo")
install.packages("xaringan")
install.packages("rmdformats")
library(Cairo)
library(xaringan)
library(rmdformats)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

